Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
clean AR_G

  # exclude rules with same course on lhs and rhs
  filter(
    lhs_course != rhs_course,
    count >= 10
    ) %>%

  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
  group_by(
    lhs_course, 
    rhs_course
    ) %>%
  top_n(
    1,
    lift
    ) %>%

>>>>

  # reduce number of rules
  filter(
    lhs_course != rhs_course, # exclude rules with same course on lhs and rhs
    count >= 5,               
    rhs_grade == 6            
    ) %>%

  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
  group_by(
    lhs_course, 
    rhs_course
    ) %>%
  top_n(
    1,
    lift
    ) %>%
  ungroup %>%
